---
title: "2nd Delivery"
author: "Eduardo Alarcón & Alfonso Pineda"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Model Fitting.

```{r}
library(readxl)
SpotifySongs <- read_excel("songstats.xlsx")
suppressWarnings(library(summarytools)) 
energy <- SpotifySongs$energy
descr(energy)

hist(energy, probability = TRUE, xlab = "Energy")
curve(dnorm(x, mean(energy), sd(energy)), col="blue", lwd=2, add=TRUE, yaxt="n")
```

```{r}
Partition <- hist(energy, plot=FALSE)
Partition

library(fitdistrplus)
normalfit <- fitdist(energy, "norm")
normalfit

CummulativeProbabilities = pnorm(c(-Inf, Partition$breaks[c(-1, -7)], Inf),
                                 normalfit$estimate[1], normalfit$estimate[2])
Probabilities = diff(CummulativeProbabilities)
Expected = length(energy)*Probabilities
chisq.test(Partition$counts, p=Probabilities)

pchisq(2.5646, 7, lower.tail = FALSE)
```

```{r}
library(nortest)
ad.test(energy)
cvm.test(energy)
lillie.test(energy)
pearson.test(energy)
sf.test(energy)

plot(normalfit)
```

# 3. Model fitting for the variable loudness

```{r}
loud <- SpotifySongs$loudness
suppressWarnings(library(summarytools)) 
descr(loud)

hist(loud, probability = TRUE, xlab="Loudness")
```


## 3.2 Fitting a Weibull distribution
```{r}
library(fitdistrplus)
weibullfit <- fitdist(loud, "weibull")
weibullfit

Partition <- hist(loud, plot=FALSE)
Partition

CummulativeProbabilities = pweibull(c(Partition$breaks[-7], Inf), weibullfit$estimate[1], weibullfit$estimate[2])
Probabilities = diff(CummulativeProbabilities)
Expected = length(loud)*Probabilities 
chisq.test(Partition$counts, p = Probabilities)

pchisq(7.0467, 6, lower.tail = FALSE)
plot(weibullfit)
```
## 3.3 Fiting Lognormal distribution

```{r}
library(fitdistrplus)
lognormalfit <- fitdist(loud, "lnorm") 
lognormalfit

Partition <- hist(loud, plot = FALSE)
Partition

CummulativeProbabilities = plnorm(c(Partition$breaks[-7], Inf), lognormalfit$estimate[1], lognormalfit$estimate[2])
Probabilities = diff(CummulativeProbabilities)
Expected = length(loud)*Probabilities 
chisq.test(Partition$counts, p = Probabilities)
plot(lognormalfit)
```

It does not seem to be as good as the normal distribution.


## 3.4 Fitting a Normal distribution to a transformation of the dataset

```{r}
library(fitdistrplus)
normalfit <- fitdistr(sqrt(loud), "normal") 
normalfit

Partition <- hist(sqrt(loud), plot = FALSE) 
Partition

CummulativeProbabilities = pnorm(c(-Inf, Partition$breaks[c(-1,-11)], Inf), normalfit$estimate[1], normalfit$estimate[2])
Probabilities = diff(CummulativeProbabilities)
Expected = length(loud)*Probabilities 
chisq.test(Partition$counts, p = Probabilities)

pchisq(9.3823, 7, lower.tail = FALSE)

hist(sqrt(loud),
probability = TRUE, # histogram has a total area = 1
xlab = "Loudness", ylim = c(0,0.2))
curve(dnorm(x, normalfit$estimate[1], normalfit$estimate[2]),
      col="blue", lwd=2, add=TRUE, yaxt="n")
```


```{r}
library(nortest) 
ad.test(sqrt(loud))

cvm.test(sqrt(loud))

lillie.test(sqrt(loud))

pearson.test(sqrt(loud), n.classes = 10)

sf.test(sqrt(loud))
```

#4. Aplication od the goodness-of-fit
### Computing using Weibull
```{r}
cat("Our data vs a normal distribution ")
pnorm(60, mean=125.8656, sd=27.0737, lower.tail=FALSE)
cat("Our data vs a weibull distribution ")
pweibull(60, shape=1.649592, scale=10.771187, lower.tail=FALSE)

```

### Computation using the Normal model applied to the square- root of the variable
```{r}
pnorm(sqrt(60), mean = 2.96006217, sd =  0.87631623 , lower.tail = FALSE)

plot(ecdf(loud))
lines(0:130, pweibull(0:130, shape = 1.649592, scale = 10.771187), col="red") 
lines(0:130, pnorm(sqrt(0:130), mean = 125.8656, sd = 27.0737), col="blue")

```
